rOpenSci tools for textmining open source science literature

### 2017-09-12 manuscript.Rmd
reworked setup to follow what we did for the gbif manuscript

# rOpenSci: tools for textmining open source science literature

## Abstract

1.  ABSTRACT PARAGRAPH 1

2.  ABSTRACT PARAGRAPH 2

3.  ABSTRACT PARAGRAPH 3

4.  ABSTRACT PARAGRAPH 4

#### Keywords

R, software, API, PLoS, Springer, Pensoft, database, textmining, opensource

Introduction
============

@@

Text mining sources
===================

@@

How to text mine from R: Three case studies
===========================================

Case study 1
------------

Case study 2
------------

Case study 3
------------

Conclusion
==========

Acknowledgements
================

@@

Appendix
========

### To read:
+ http://lintool.github.com/MapReduceAlgorithms/index.html
+

>>>>

---
layout: review, 11pt
linenumbers: true
title: "rOpenSci tools for textmining open source science literature"
author:
  - name: Scott Chamberlain
    affiliation: cstar
    email: scott(at)ropensci.org
    footnote: Corresponding author
address:
  - code: cstar
    address: |
      rOpenSci, Museum of Paleontology, University of California, Berkeley, CA, USA
abstract: |
      Corresponding Author:

      Scott Chamberlain

      rOpenSci, Museum of Paleontology, University of California, Berkeley, CA, USA

      Email address: [scott@ropensci.org](mailto:scott@ropensci.org)

      \newpage

      Background. xxxx.

      Methods. xxxx.

      Results. xxxx.

      Discussion. xxxx.

bibliography: components/references.bib
csl: components/peerj.csl
documentclass: components/elsarticle

output:
  pdf_document:
    template: components/elsarticle.latex
    keep_tex: true
    fig_caption: true
---

```{r compile-settings, include=FALSE}
library("methods")
library("knitr")
opts_chunk$set(
  tidy = FALSE,
  warning = FALSE,
  message = FALSE,
  cache = 1,
  comment = '#>',
  collapse = TRUE,
  verbose = TRUE
)

basename <- gsub(".Rmd", "", knitr:::knit_concord$get('infile'))
opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
               cache.path = paste("components/cache/", basename, "/", sep=""))

# tibble options
options(tibble.max_extra_cols = 10)
```

\newpage

# Introduction

@@

# Text mining sources

@@

# How to text mine from R: Three case studies

### Case study 1

```{r city-diversity, child="use-cases/city-diversity.Rmd", eval=FALSE}
```

### Case study 2

```{r city-diversity, child="use-cases/city-diversity.Rmd", eval=FALSE}
```

### Case study 3

```{r city-diversity, child="use-cases/city-diversity.Rmd", eval=FALSE}
```

# Conclusions and future directions

# Acknowledgments

# Data Accessibility

All scripts and data used in this paper can be found in the permanent
data archive Zenodo under the digital object identifier (DOI). This DOI
corresponds to a snapshot of the GitHub repository at
<https://github.com/ropensci/textmine>. Software can be found at
<https://github.com/ropensci/xxx>, xxxx, all under MIT licenses.

@@
